\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-02-16 article.tex
Fixed \notin
Fixed wording and grammar

  $a \in S$ denotes that the object $a$ is a member of the set $S$. If $a$
  is not a member of S, we write $a \not \in S$.

@@

  \[
    S - T = \{x:x \in S \: and \: x \not \in T\}
  \]

@@

  \[
    S \Delta T = \{x:(x \in S \: and \: x \not \in T) \: or \: (x \in T \: and
    \: x \not \in S)\}
  \]

@@

  In this section we describe where the data originates. Next we elaborate on
  the approach taken to register and investigate the dataset. Finally, a look
  at how each movement has been classified with emphasis on special cases.

@@

  Suitable tags were attached to every movement by first extracting keywords
  from their English description, and then adding more detailed tags while
  performing the pattern.

@@

  Classification is done by attaching metadata, in terms of tags, to each
  pattern movement.

@@

  The implications of tagging movements with $\{left\_technique, \:
  right\_technique\}$ is that the total amount of hand techniques on either
  side are higher than what actually is the case. This flaw does not affect
  the bias we are investigating.

>>>>

  $a \in S$ denotes that the object $a$ is a member of the set $S$. If $a$
  is not a member of S, we write $a \notin S$.

@@

  \[
    S - T = \{x:x \in S \: and \: x \notin T\}
  \]

@@

  \[
    S \Delta T = \{x:(x \in S \: and \: x \notin T) \: or \: (x \in T \: and
    \: x \notin S)\}
  \]

@@

  In this section we describe where the data originates. Next we elaborate on
  the approach taken to register and investigate the dataset. Finally, we look
  at how each movement has been classified with emphasis on special cases.

@@

  Suitable tags were then attached to every movement by first extracting
  keywords from their English description, and then adding more detailed tags
  while performing the pattern.

@@

  Classification was done by attaching metadata, in terms of tags, to each
  pattern movement.

@@

  The implications of tagging movements with $\{left\_technique, \:
  right\_technique\}$ is that the total amount of hand techniques on either
  side are higher than what actually is the case. This flaw does not affect
  the bias we are investigating, though.
